---
title: "PSTAT 120B: Mathematical Statistics, I"
subtitle: "Lectures and Course Schedule"
author:
  - name: "Ethan Marzban"
    affiliations:
      - name: "Summer Session A, 2024"
author-title: "Instructor"
affiliation-title: "Quarter"
format: html
---



## Lecture Slide Decks

-   <a href="../Files/Lectures/0_Why_Stats.pdf" target="_blank">**Topic 0:** An Introduction to the Course </a>

-   <a href="../Files/Lectures/1_Cond_Expec_Dist.pdf" target="_blank">**Topic 1:** Conditional Distributions and Expectations </a> [Updated 6/26/24]

-   **Topic 2: Transformations**
    -   <a href="../Files/Lectures/2_Transformations_1.pdf" target="_blank">**Part 1 (CDF Method)**</a>


\

## Homework Assignments

-   <a href="../Files/HW/HW01.pdf" target="_blank">**HW01**:</a> Due by 11:59pm on Wednesday, June 26, 2024 on Gradescope


\

## Course Schedule 

:::{.callout-warning}
## **Note**

_**This page will be updated as we progress through the quarter; please check back regularly for updates!**_
:::

:::{.callout-note}
## **Emoji Meanings**
-   🧑‍🏫 = Lecture
-   📖 = Textbook Reading
-   📄 = Discussion Section Worksheet
:::

```{r setup, include = F}
library(googlesheets4)
library(gt)
library(tidyverse)

gs4_deauth()

temp_sheet <- read_sheet("https://docs.google.com/spreadsheets/d/1W9NhgxlZsbb-JW6W5nu8a_7OmF42WV6T3hyfb4PMvLY/edit?usp=sharing")
```

```{r}
#| echo: False

temp_sheet %>%
  select(-Admin_Notes, -Day) %>%
  mutate(Date = as.Date(Date)) %>%
  gt() %>%
  fmt_date(Date, date_style = 31) %>%
  sub_missing(columns = c(Week, `Textbook Sections`, Topic, `Corresponding Slide Deck`, `Section Materials / Things Due`), missing_text = "") %>%
  tab_style(
    style = cell_borders(
      sides = "right",
      color = "#D3D3D3",
      style = "solid"
    ),
    locations = cells_body(
      columns = c(Date, Topic, `Textbook Sections`, `Corresponding Slide Deck`, `Section Materials / Things Due`)
    )
  ) %>%
  cols_align(
    align = "center", 
    columns = c(Week)
  ) %>%
  cols_align(
    align = "right", 
    columns = c(Date)
  ) %>%
  cols_align(
    align = "left", 
    columns = c(`Corresponding Slide Deck`)
  ) %>%
  cols_align(
    align = "left", 
    columns = c(`Section Materials / Things Due`)
  ) %>%
  fmt_markdown(
    columns = c(Week, `Textbook Sections`, Topic, `Corresponding Slide Deck`, `Section Materials / Things Due`)
  ) %>%
  cols_width(
    Week ~ pct(7),
    Date ~ pct(13), 
    `Textbook Sections` ~ pct(20),
    Topic ~ pct(30),
    `Corresponding Slide Deck` ~ pct(18),
    `Section Materials / Things Due` ~ pct(12)
  ) %>%
  cols_label_with(fn = function(x) {
      janitor::make_clean_names(x, case = "title") %>%
        toupper() %>%
        stringr::str_replace_all("^|$", "**") %>%
        md()
    }) %>%
  tab_options(table.font.size = 16) %>%
  opt_row_striping()
```

### Some More Information

-   Midterm exams take place on Wednesdays (twice throughout the quarter, on the dates listed in the calendar above).
-   Homework assignments are due on Wednesdays in non-exam weeks, and on Tuesdays in exam weeks.
-   Quizzes take place **synchronously** and **in-person**, during the first 20 minutes of Thursday Discussion Sections (on the dates outlined in the calendar above).
-   I recommend reading the corresponding Textbook sections _before_ coming to lecture.
