---
title: "PSTAT 120B: Mathematical Statistics, I"
subtitle: "Lectures and Course Schedule"
author:
  - name: "Ethan Marzban"
    affiliations:
      - name: "Summer Session A, 2024"
author-title: "Instructor"
affiliation-title: "Quarter"
format: html
---



## Lecture Slide Decks

-   <a href="../Files/Lectures/0_Why_Stats.pdf" target="_blank">**Topic 0:** An Introduction to the Course </a>

-   <a href="../Files/Lectures/1_Cond_Expec_Dist.pdf" target="_blank">**Topic 1:** Conditional Distributions and Expectations </a> [Updated 6/26/24]

-   **Topic 2: Transformations**
    -   <a href="../Files/Lectures/2_Univariate_Transformations.pdf" target="_blank">**Univariate Transformations**</a> (these are fair game for the first midterm)
        -   <a href="../Files/Lectures/0_Monotonicity.pdf" target="_blank">**Review of Precalculus:** Monotonicity</a> (please note that I expect you to know these terms from prerequisite classes; feel free to ask me (or the TAs) about them in Office Hours!)
    -   <a href="../Files/Lectures/2_Transformations_Multi.pdf" target="_blank">**Multivariate Transformations**</a> [Updated 7/9/24]

-   **Topic 3: Estimation**
    -   <a href="../Files/Lectures/3_Estimation_P1.pdf" target="_blank">**Part 1**</a> (these slides will be updated periodically, so please check back regularly!) [Last updated: 7/10/24]
    
    -   <a href="../Files/Lectures/3_Estimation2.pdf" target="_blank">**Part 2**</a> (more work will be done on the whiteboard) [Last updated: 7/11/24]
    
    -   <a href="../Files/Lectures/3_Estimation3.pdf" target="_blank">**Part 3**</a> [Last updated: 7/15/24]

\

## Homework Assignments

-   <a href="../Files/HW/HW01.pdf" target="_blank">**HW01**:</a> Due by 11:59pm on Wednesday, June 26, 2024 on Gradescope
    -   **Solutions**: <a href="../Files/HW/HW01_Solns.pdf" target="_blank"><button type="button" class="btn btn-info">.PDF</button></a>
    
\

-   <a href="../Files/HW/HW02.pdf" target="_blank">**HW02**:</a> Due by 11:59pm on Tuesday, July 2, 2024 on Gradescope
    -   **Solutions**: <a href="https://drive.google.com/file/d/1ALa8AHNZjbrL1zgF5lcZLj3Dfr-wjbqi/" target="_blank"><button type="button" class="btn btn-info">Link</button></a>

\

-   <a href="../Files/HW/HW03.pdf" target="_blank">**HW03**:</a> Due by 11:59pm on Wednesday, July 10, 2024 on Gradescope
    -   **Solutions** can be found at [this](https://ucsb.instructure.com/courses/20787/modules) link, and <a href="https://drive.google.com/file/d/17bHbRujD7hOjLUvfUQibIIfCAh6YN9QB/" target="_blank"><button type="button" class="btn btn-info">here</button></a>
    
\

-   <a href="../Files/HW/HW04.pdf" target="_blank">**HW04**:</a> Due by 11:59pm on Monday, July 15, 2024 on Gradescope
    
\

## Quiz Information


-   **Quiz02:** 
    -   **Topics Covered**: All of Topic 2.5 (Bivariate and Multivariate Transformations)
    -   **Formula Sheet**: <a href="../Files/Misc/Quiz02_Formula_Sheet.pdf" target="_blank"><button type="button" class="btn btn-info">.PDF</button></a>
    -   **Solutions**: <a href="../Files/QzSolns/Qz02_Solns.pdf" target="_blank"><button type="button" class="btn btn-info">.PDF</button></a> 
    
\

-   **Quiz01:** 
    -   **Topics Covered**: All of Topic 01 (including conditional expectations; just know it at the level of the coin-and-die example)
    -   **Coverpage and Formula Sheet**: <a href="../Files/Misc/Quiz01_Coverpage.pdf" target="_blank"><button type="button" class="btn btn-info">.PDF</button></a>
    -   **Solutions**: <a href="../Files/QzSolns/Qz01_Solns.pdf" target="_blank"><button type="button" class="btn btn-info">.PDF</button></a> 
    
    Please note: there were several versions of the quiz that differed only slightly (in numbers and problem contexts). I will typically only be posting solutions to one version, again because the different versions were very similar to one another. You're welcome to bring questions about your specific quiz to Office Hours (either the Instructor's or the TAs')!

## Course Schedule 

:::{.callout-warning}
## **Note**

_**This page will be updated as we progress through the quarter; please check back regularly for updates!**_
:::

:::{.callout-note}
## **Emoji Meanings**
-   🧑‍🏫 = Lecture
-   📖 = Textbook Reading
-   📄 = Discussion Section Worksheet
:::

_**Last Updated:**_ 7/3/24

```{r setup, include = F}
library(googlesheets4)
library(gt)
library(tidyverse)

gs4_deauth()

temp_sheet <- read_sheet("https://docs.google.com/spreadsheets/d/1W9NhgxlZsbb-JW6W5nu8a_7OmF42WV6T3hyfb4PMvLY/edit?usp=sharing")
```

```{r}
#| echo: False

temp_sheet %>%
  select(-Admin_Notes, -Day) %>%
  mutate(Date = as.Date(Date)) %>%
  gt() %>%
  fmt_date(Date, date_style = 31) %>%
  sub_missing(columns = c(Week, `Textbook Sections`, Topic, `Corresponding Slide Deck`, `Section Materials / Things Due`), missing_text = "") %>%
  tab_style(
    style = cell_borders(
      sides = "right",
      color = "#D3D3D3",
      style = "solid"
    ),
    locations = cells_body(
      columns = c(Date, Topic, `Textbook Sections`, `Corresponding Slide Deck`, `Section Materials / Things Due`)
    )
  ) %>%
  cols_align(
    align = "center", 
    columns = c(Week)
  ) %>%
  cols_align(
    align = "right", 
    columns = c(Date)
  ) %>%
  cols_align(
    align = "left", 
    columns = c(`Corresponding Slide Deck`)
  ) %>%
  cols_align(
    align = "left", 
    columns = c(`Section Materials / Things Due`)
  ) %>%
  fmt_markdown(
    columns = c(Week, `Textbook Sections`, Topic, `Corresponding Slide Deck`, `Section Materials / Things Due`)
  ) %>%
  cols_width(
    Week ~ pct(7),
    Date ~ pct(13), 
    `Textbook Sections` ~ pct(20),
    Topic ~ pct(30),
    `Corresponding Slide Deck` ~ pct(18),
    `Section Materials / Things Due` ~ pct(12)
  ) %>%
  cols_label_with(fn = function(x) {
      janitor::make_clean_names(x, case = "title") %>%
        toupper() %>%
        stringr::str_replace_all("^|$", "**") %>%
        md()
    }) %>%
  tab_options(table.font.size = 16) %>%
  opt_row_striping()
```

### Some More Information

-   Midterm exams take place on Wednesdays (twice throughout the quarter, on the dates listed in the calendar above).
-   Homework assignments are due on Wednesdays in non-exam weeks, and on Tuesdays in exam weeks.
-   Quizzes take place **synchronously** and **in-person**, during the first 20 minutes of Thursday Discussion Sections (on the dates outlined in the calendar above).
-   I recommend reading the corresponding Textbook sections _before_ coming to lecture.
